---
title: "MAPm Pretest Fall 19 Calibration V2"
date: "1/28/2020"
output: 
  html_document:
    toc: true
    toc_float: true
---

### 1. MAPm Consruct Map
<a href="https://nmsi.bear-apps.com/constructs/public/mBIW9MLhlSuMMGzpYb9keiDD5wqvvK" target = "_blank">Link </a> to construct map


### 2. Items & Scoring Guides
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/263/bundle/360/assignments/5746/score" target = "_blank">Cycle.03a </a> (scroll down)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/316/activities/261/item/5320/assignments/score" target = "_blank">Glow.1a </a>
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/259/bundle/355/assignments/5219/score" target = "_blank">Glow.2a-2c </a>
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/340/item/5536/assignments/5482/score" target = "_blank">Powder.5b.MC </a>
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/340/item/5696/assignments/score" target = "_blank">Straw.4a </a> 
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/264/item/4944/assignments/score" target = "_blank">Tshirt.7a </a>


```{r setup, include=FALSE}
require(WrightMap)
require(tidyverse)
require(RColorBrewer)
require(knitr)
require(kableExtra)

knitr::opts_chunk$set(echo = TRUE)

# read CQ result files
model1 <- CQmodel(p.est = "data1/MAPmWLEcases.txt", show = "data1/MAPmWLEshowV2.txt")

# setting theta for WrightMap1 (x-axis = items) and WrightMap2 (x-axis = thresholds)
theta1 <- model1$p.est$`est (d1)`

# make thresholds dataframe (thres1) and order by item name 
thres1 <- make.thresholds(model1) %>% 
  as.data.frame() %>% 
  rownames_to_column(., "item") %>%
  arrange(item) %>% 
  mutate(V4 = NA)

View(thres1)

# manually correcting threshold placement for items with skipped lvl

## Glow.01a (L1, L3, L4)
thres1[2, 4] <- thres1[2, 2]
thres1[2, 5] <- thres1[2, 3]
thres1[2, 2] <- NA
thres1[2, 3] <- NA

## Glow.02a (L1, L2, L3 -- no L0)
thres1[3, 4] <- thres1[3, 3]
thres1[3, 3] <- thres1[3, 2]
thres1[3, 2] <- NA

## Powder.05ab (L1, L3, L4)
thres1[6, 4] <- thres1[6, 2]
thres1[6, 5] <- thres1[6, 3]
thres1[6, 2] <- NA
thres1[6, 3] <- NA


# give descriptive col names for thres1
colnames(thres1) <- c("item", "L1", "L2 ", "L3", "L4")

# get rid of item col for WrightMap 1
thres1a <- thres1 %>% select(-item)

# set item names for WrightMap1 (x-axis = items)
itemnames <- thres1$item

#transposing thres1 to tt for WrightMap 2 with thresfolds on x-axis (rather than items)  
#transposing thres1 to tt for WrightMap 2 with thresfolds on x-axis (rather than items)  
tt <- thres1 %>%
  gather(var, value, -item) %>% 
  spread(item, value) 

dim(tt) # 4 x 9

# subset tt (dropping the first column)
tt <- tt[(1:4), (2:9)]

# set itemnames2 for x-axis label for WrightMap2
itemnames2 <- c("L0 vs.L1", "L1 vs.L2", "L2 vs.L3", "L3 vs.L4")

# set colors; note the number before the closing parenthesis
# is the number of items
thresholds.colors <- data.frame(
  l1 = rep( "#D7191C", 8),
  l2 = rep( "#FDAE61",8),
  l3 = rep( "#ABDDA4",8),
  l4 = rep( "#2B83BA",8))

itemcolors <- c("#D7191C", "#FDAE61", "#ABDDA4", "#2B83BA")

```

### 3. Wright Maps

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}

#WrightMap1 with items on x-axis
wrightMap(theta1, thres1a, 
          label.items = itemnames,
          main.title   = "Wright Map: MAPm (by item)",
          label.items.srt = 90,
          axis.items = "",
          thr.sym.col.bg = thresholds.colors)

# mean(model1$p.est$`est (d1)`)
# sd(model1$p.est$`est (d1)`)

# WrightMap 2 with thresfolds on x-axis
wrightMap(theta1, tt,
          label.items = itemnames2,
          main.title   = "Wright Map: MAPm (by thresholds)",
          thr.sym.col.fg = itemcolors,
          thr.sym.col.bg = itemcolors,
          axis.items = "threshold")

```

```{r calib.results, echo=FALSE, results = FALSE}
n.cases <- length(theta1)
n.items <- length(thres1$item)
wle.rel <- model1$rel.coef[[2]]
eap.rel <- model1$rel.coef[[3]]
min.Wfit <- min(model1$RMP$item$W.fit)
max.Wfit <- max(model1$RMP$item$W.fit)
```
#####   Calibration stats from calibration

*  `r n.cases` cases
*  `r n.items` scorable "units"
*  WLE Separation Reliability: `r wle.rel`
*  EAP/PV Reliability: `r eap.rel`
*  Weighted MNSQ range: `r min.Wfit` - `r max.Wfit`


### 4. Threshold Difficulty

```{r tables, echo=FALSE, message = FALSE, warning = FALSE}

knitr::kable(thres1, format = "html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, font_size = 12)

```


### 5. Item Analysis

* <a href="https://drive.google.com/open?id=1WZifZWOh17hMDVK8A_cmf1q1no-eLCF-" target = "_blank">Link to Item Analysis </a> (ConQuest output)
