---
title: "IMR Pretest Fall 19 Calibration #1 & #2"
date: "12/5/2019"
output: html_document
---

On this page, you will find the following: 

1. IMR (interpreting mathematical results) Construct Map,
2. Items & Scoring Guides, 
3. WrightMaps, 
4. Thresfold Estimates, 
5. A link to Item Analysis (from ConQuest), and
6. A link to <a href="http://standardsmaps.com:3838/smap/" target = "_blank">StandardsMaps </a>software (for standards setting).

### <a href="https://nmsi.bear-apps.com/constructs/public/fUft37Rtk3i21xShtnnOf6gJRM4CQR" target = "_blank">1. IMR Construct Map </a>

* PDF of Construct Map, Items, and Scoring Guides is <a href="https://drive.google.com/open?id=10rKmoXhOzdaM8wFAab_11a6PFIP7HTBS" target = "_blank">here </a> 


### 2. IMR Items & Scoring Guides on BASS
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/344/bundle/388/assignments/5342/score" target = "_blank">Airline.03a </a> (L3 is the most difficult; item stem needs to be changed to prompt desired responses)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/259/item/5328/assignments/score" target = "_blank">Crude.06ab </a> (prompt should be improved to make students focus on decreasing trends)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/264/bundle/360/assignments/5741/score" target = "_blank">Cycle.04ab </a> (Scroll down to the last 2 questions; L1 & L2  not much separation)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/340/item/5769/assignments/5482/score" target = "_blank">Garden5abc </a> (Scroll down to the last 3 questions; initially 5a was too difficult as L1 and no L2 vs L3 distinction in 5bc)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/294/activities/346/item/5607/score" target = "_blank">Hiring 3ab </a> (L1, L2, L3 no separation)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/259/bundle/313/assignments/5219/score" target = "_blank">Pest.05ab </a> (scroll down to middle; L1 & L2  not much separation)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/261/bundle/356/assignments/5119/score" target = "_blank">Population.07a </a> (scroll down to the bottom)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/340/bundle/385/assignments/5482/score" target = "_blank">Powder.06a </a> (scroll down to the bottom)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/261/item/5349/assignments/score" target = "_blank">Wildlife.02_OE </a> (L1 too easy; only 2 people scored into 0)
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/259/bundle/354/assignments/5219/score" target = "_blank">Word.03_MC </a> (L1 too easy; only 2 people scored into 0)



```{r setup, include=FALSE}
require(WrightMap)
require(tidyverse)
require(readxl)
library(RColorBrewer)
library(knitr)
require(kableExtra)

knitr::opts_chunk$set(echo = TRUE)

# read CQ result files
model1 <- CQmodel(p.est = "data/IMRWLEcases.txt", show = "data/IMR.WLE.shw.txt")

# setting theta for WrightMap1 (x-axis = items) and WrightMap2 (x-axis = thresholds)
theta1 <- model1$p.est$`est (d1)`

# make thresholds dataframe (thres1) and order by item name 
thres1 <- make.thresholds(model1) %>% 
  as.data.frame() %>% 
  rownames_to_column(., "item") %>%
  arrange(item)

View(thres1)

# give descriptive col names for thres1
colnames(thres1) <- c("item", "L1", "L2 ", "L3", "L4")

# get rid of item col for WrightMap 1
thres1a <- thres1 %>% select(-item)

# set item names for WrightMap1 (x-axis = items)
itemnames <- thres1$item

#transposing thres1 to tt for WrightMap 2 with thresfolds on x-axis (rather than items)  
tt <- thres1 %>%
  select(-item) %>% 
  rownames_to_column %>% 
  gather(var, value, -rowname) %>% 
  spread(rowname, value) 

# manually match col names; careful as col num 1, 10, 11, and then 2, 3, ...
colnames(tt) <- c("", "air3a", "wild2", "word3", "cru6ab", "cyc4ab", "gar5a", "gar5bc", "hir3ab", "pes5ab", "pop7a",  "pow6ab")

row.names(tt) <- NULL
View(tt)
dim(tt) # 4 rows, 12 cols

# subset tt (dropping the first column)
tt <- tt[(1:4), (2:12)]

# set itemnames2 for x-axis label for WrightMap2
itemnames2 <- c("L0 vs.L1", "L1 vs.L2", "L2 vs.L3", "L3 vs.L4")

# set colors
thresholds.colors <- data.frame(
  l1 = rep( "#D7191C", 11),
  l2 = rep( "#FDAE61",11),
  l3 = rep( "#ABDDA4",11),
  l4 = rep( "#2B83BA",11))

itemcolors <- c("#D7191C", "#FDAE61", "#ABDDA4", "#2B83BA")

```

### 3a. Initial WrightMaps (from Calibration 1)

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}

#WrightMap1 with items on x-axis
wrightMap(theta1, thres1a, 
          label.items = itemnames,
          main.title   = "Wright Map: IMR (by item)",
          label.items.srt = 90,
          axis.items = "",
          thr.sym.col.bg = thresholds.colors)

# mean(model1$p.est$`est (d1)`)
# sd(model1$p.est$`est (d1)`)

# WrightMap 2 with thresfolds on x-axis
wrightMap(theta1, tt,
          label.items = itemnames2,
          main.title   = "Wright Map: IMR (by thresholds)",
          thr.sym.col.fg = itemcolors,
          thr.sym.col.bg = itemcolors,
          axis.items = "threshold")

```

### 3b. WrightMap after Item Investigations (from Calibration 2)

* Reduced overlap between L1 and L2 by making Garden 5a's thresfold to be L3 (initially it was misplaced at L1)
* Reduced overlap between L2 and L3 by getting rid of partial credits in Garden 5bc & Hiring3ab
* Cycle4ab has some issues with scoring guides (no separation between L1 and L2).A similar issue may exist with Pest5ab.
* The first threshold for Wild2 and Word3 (both very low) should probably be ignored as they are based on only two people scoring into 0. 

```{r plots2, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}

# get calibration #2 results from standard setting data
load("~/Dropbox/NMSI/0.GitHub/nmsi_wrightmaps_fall19/data/NMSI-IMR.rdata")

deltas <- sets$deltas 

thres2 <- make.thresholds(deltas) %>% 
  as.data.frame()

# hand correcting level placement

## hiring
thres2[11, 3] <- thres2[11, 1]
thres2[11, 1] <- NA

## garden3bc
thres2[8, 3] <- thres2[8, 1]
thres2[8, 1] <- NA

## garden 3a
thres2[7, 3] <- thres2[7, 1]
thres2[7, 1] <- NA

## make rowname as name var
thres2 <- tibble::rownames_to_column(thres2, "item")
colnames(thres2) <- c("name", "L1", "L2 ", "L3", "L4")

#transposing to have thresfolds on x-axis (rather than items) 
tt2 <- thres2 %>%
  select(-name) %>% 
  rownames_to_column %>% 
  gather(var, value, -rowname) %>% 
  spread(rowname, value) 

colnames(tt2) <- c("", "cru6ab", "air3a", "hir3ab", "word3", "cyc4ab", "pes5ab", "wild2", 
                   "pop7a", "gar5a", "gar5bc",  "pow6ab")

row.names(tt2) <- NULL
tt2 <- tt2[(1:4), (2:12)]

thres2 <- thres2 %>%
    arrange(name)

theta2 <- sets$thetas$d1

# WrightMap1 with items on x-axis
wrightMap(theta2, thres2[, 2:5], 
          label.items = itemnames,
          main.title   = "Revised Wright Map: IMR (by item)",
          label.items.srt = 90,
          axis.items = "",
          thr.sym.col.bg = thresholds.colors)

# WrightMap2 with thresfolds on x-axis
wrightMap(theta2, tt2,
          label.items = itemnames2,
          main.title   = "Revised Wright Map: IMR (by thresholds)",
          thr.sym.col.fg = itemcolors,
          thr.sym.col.bg = itemcolors,
          axis.items = "threshold")

```

#####   Calibration stats from calibration run #2

*  808 cases
*  11 scorable "units"
*  WLE Separation Reliability: 0.192 (run#1: 0.167)
*  EAP/PV Reliability: 0.355 (run#1: 0.378)
*  Weighted MNSQ: 0.91 - 1.07 (run#1: 1.90-1.14)


### 4. Threshold difficulty estimates (from Calibration 2)

```{r tables, echo=FALSE, message = FALSE, warning = FALSE}

knitr::kable(thres2, format = "html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, font_size = 12)

```


### 5. Item Analysis (from Calibration 2)

* <a href="https://drive.google.com/open?id=1yjXX3IIb4Mwysgn6B1t_pq4nOL1b_u7K" target = "_blank">Link to Item Analysis </a> (ConQuest output from Run #2 after revisions)


### 6. StandardsMaps Software


*  <a href="http://standardsmaps.com:3838/smap/" target = "_blank">Link to StandardsMaps </a> software (for standards setting)

*  You need to download <a href="https://drive.google.com/file/d/1CQwvoDIQNjjj1IFt02M_25nxkxVZjumM/view?usp=sharing" target = "_blank">NMSI-IMR.rdata </a> to your machine and upload it to StandardsMaps.

*   <a href="https://drive.google.com/open?id=1apjNDvdnZY5Y-dAP0W1db4d8BAcUBfJU" target = "_blank">Instruction </a> for setting up StandardsMaps on your machine.






