---
title: "PRA Pretest Fall 19 Calibration #1 Results"
date: "12/29/2019"
output: html_document
---

On this page, you will find the following: 

1. PRA (interpreting mathematical results) Construct Map,
2. Items & Scoring Guides, 
3. WrightMaps, 
4. Thresfold Estimates, 
5. A link to Item Analysis (from ConQuest), and


### <a href="https://nmsi.bear-apps.com/constructs/public/w48UWWjseeXIVh433HTf5F9aXEjxML" target = "_blank">1. PRA Construct Map </a>


### 2. PRA Items & Scoring Guides on BASS
* <a href="https://nmsi.bear-apps.com/scheduled_activities/316/activities/261/bundle/339/assignments/6321/score" target = "_blank">Brake.1a_MC & 2a_MC </a> 
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/340/item/5628/assignments/score" target = "_blank">Brake.2c_MC </a> 
* <a href="https://nmsi.bear-apps.com/scheduled_activities/316/activities/263/bundle/340/assignments/6385/score" target = "_blank">Brake.4a_NU & 4b_MC </a> 
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/340/item/5633/assignments/5482/score" target = "_blank">Brake.4b_OE </a> 
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/344/bundle/234/assignments/5342/score" target = "_blank">Water.1_MCOE </a>
* <a href="https://nmsi.bear-apps.com/scheduled_activities/294/activities/340/item/5616/assignments/score" target = "_blank">Word.1_MC </a>
* <a href="https://nmsi.bear-apps.com/scheduled_activities/308/activities/260/bundle/354/assignments/5802/score" target = "_blank">Word.4a_OE & 4b_OE </a>


```{r setup, include=FALSE}
require(WrightMap)
require(tidyverse)
require(readxl)
library(RColorBrewer)
library(knitr)
require(kableExtra)

knitr::opts_chunk$set(echo = TRUE)

model1 <- CQmodel(p.est = "data/PRAWLEcases.txt", show = "data/PRAWLEshow.txt")

# setting theta for WrightMap1 (x-axis = items) and WrightMap2 (x-axis = thresholds)
theta1 <- model1$p.est$`est (d1)`

# make thresholds dataframe (thres1) and order by item name 
thres1 <- make.thresholds(model1) %>% 
  as.data.frame() %>% 
  rownames_to_column(., "item") %>%
  arrange(item)

View(thres1)

# give descriptive col names for thres1
colnames(thres1) <- c("item", "L2 ", "L3")

# get rid of item col for WrightMap 1
thres1a <- thres1 %>% select(-item)

#transposing thres1 to tt for WrightMap 2 with thresfolds on x-axis (rather than items) 
tt <- thres1 %>%
  select(-item) %>% 
  rownames_to_column %>% 
  gather(var, value, -rowname) %>% 
  spread(rowname, value) 

# give descriptive col names = short item names
colnames(tt) <- c("", "brak1aM", "word.4bO", "brak2aM", "brak2cM", "brak4aN", "brak4bM", 
                  "brak4bO", "water1M", "word1M", "word4aO")
row.names(tt) <- NULL
View(tt)

# subset tt (dropping the first column)
tt <- tt[(1:2), (2:11)]

# itemnames2 will be used for WrightMap 2
itemnames2 <- c("0-1 vs.L2", "L0-2 vs.L3")

# set item names and thresholds colors for WrightMap1 (x-axis = items)
itemnames <- thres1$item

thresholds.colors <- data.frame(
  l2 = rep( "#FDAE61",nrow(thres1)),
  l3 = rep( "#ABDDA4",nrow(thres1)))

# set item colors for WrightMap2 (x-axis = thresholds)
itemcolors <- c("#FDAE61", "#ABDDA4") #selecting only L2 and L3 clors
# itemcolors <- c("#D7191C", "#FDAE61", "#ABDDA4", "#2B83BA") here are all four colors for 4 levels

```

### 3. WrightMaps

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}

#WrightMap1 with items on x-axis
wrightMap(theta1, thres1a, 
          label.items = itemnames,
          main.title   = "Wright Map: PRA (by item)",
          label.items.srt = 90,
          axis.items = "",
          dim.names = "",
          thr.sym.col.bg = thresholds.colors)

# mean(model1$p.est$`est (d1)`)
# sd(model1$p.est$`est (d1)`)


# WrightMap2 with thresfolds on x-axis
wrightMap(theta1, tt,
          label.items = itemnames2,
          main.title   = "Wright Map: PRA (by thresholds)",
          dim.names = "",
          thr.sym.col.fg = itemcolors,
          thr.sym.col.bg = itemcolors,
          axis.items = "threshold")

```


#####   Calibration stats from calibration

*  815 cases
*  10 scorable "units"
*  WLE Separation Reliability: 0.192
*  EAP/PV Reliability: 0.47
*  Weighted MNSQ: 0.86 - 1.13


### 4. Threshold difficulty estimates

```{r tables, echo=FALSE, message = FALSE, warning = FALSE}

knitr::kable(thres1, format = "html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, font_size = 12)

```


### 5. Item Analysis

* <a href="https://drive.google.com/open?id=1WWhkq18o3RfS-yZc1fe7fPV4rT0p1rUr" target = "_blank">Link to Item Analysis </a> (ConQuest output)
